Planarity and Street Network Representation in Urban Form Analysis

### 2018-03-02 main.tex
edits for submission

\documentclass[Afour,sageh,times]{sagej}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[USenglish]{babel}
\usepackage{microtype}
\usepackage{booktabs}
\usepackage{setspace}
\usepackage{csquotes}
\usepackage{url}
\usepackage{moreverb}
\usepackage[hidelinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red]{hyperref}
\newcommand\BibTeX{{\rmfamily B\kern-.05em \textsc{i\kern-.025em b}\kern-.08em T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

@@

\usepackage[final]{draftwatermark}
\SetWatermarkText{DRAFT}
\SetWatermarkScale{1}
\SetWatermarkLightness{0.9}

@@

\runninghead{Author Redacted}
\title{Planarity and Street Network Representation in Urban Form Analysis}
\author{Author Redacted\affilnum{1}}
\affiliation{\affilnum{1}Affiliation redacted}
\corrauth{Author Redacted, Address Redacted}
\email{Email Redacted}

@@

\begin{figure}[tbp]
	\includegraphics[width=0.48\textwidth]{figures/planar_vs_not_labels.png}
	\caption{Spatial network examples. Gray lines = edges (i.e., street segments), circles = nodes (i.e., intersections and dead ends), red dots = two-dimensional line crossings (i.e., artificial nodes in planar representation).}
	\label{fig:planar_vs_not}
\end{figure}

@@

\begin{table*}[htbp]
	\centering
	\caption{Planarity measures for central street networks in 50 cities worldwide (Planar = whether street network passed the formal test of planarity; $\phi$ = Spatial Planarity Ratio; $\lambda$ = Edge Length Ratio).}
	\label{tab:world_cities}
	\input{tables/table_world_cities.tex}
\end{table*}

\begin{figure*}[htbp]
	\centering
	\includegraphics[width=\textwidth]{figures/world_map_bw.png}
	\caption{Map of world cities from Table \ref{tab:world_cities} grouped by drivable $\phi$ terciles (lower values mean less planar).}
	\label{fig:world_map_bw}
\end{figure*}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=0.48\textwidth]{figures/regression_lambda_phi_linear.png}
	\caption{Plot of $\lambda$ vs $\phi$ by network type with regression lines.}
	\label{fig:regression_lambda_phi}
\end{figure}

@@

\begin{table}[htbp]
	\centering
	\caption{Summary statistics of planarity indicators across 100 square-mile samples of Oakland, California's drivable network.}
	\label{tab:samples_city}
	\input{tables/table_samples_city.tex}
\end{table}

@@

%\clearpage
\bibliographystyle{apalike}
\bibliography{references}

>>>>

\documentclass[Afour,doublespace,sageh,times]{sagej}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[USenglish]{babel}
\usepackage{microtype}
\usepackage{booktabs}
\usepackage{setspace}
\usepackage{csquotes}
\usepackage{url}
\usepackage[colorlinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red]{hyperref}

@@

@@

\runninghead{}
\title{Planarity and Street Network Representation in Urban Form Analysis}
\author{}
\affiliation{}
\corrauth{}
\email{}

@@

\begin{figure}[tbp]
	\centering
	\includegraphics[width=0.48\textwidth]{fig_planar_vs_not_labels.png}
	\caption{Spatial network examples. Gray lines = edges (i.e., street segments), circles = nodes (i.e., intersections and dead ends), red dots = two-dimensional line crossings (i.e., artificial nodes in planar representation).}
	\label{fig:planar_vs_not}
\end{figure}

@@

\begin{table*}[htbp]
	\centering
	\caption{Planarity measures for central street networks in 50 cities worldwide (Planar = whether street network passed the formal test of planarity; $\phi$ = Spatial Planarity Ratio; $\lambda$ = Edge Length Ratio).}
	\label{tab:world_cities}
	\input{table_world_cities.tex}
\end{table*}

\begin{figure*}[htbp]
	\centering
	\includegraphics[width=\textwidth]{fig_world_map_bw.png}
	\caption{Map of world cities from Table \ref{tab:world_cities} grouped by drivable $\phi$ terciles (lower values mean less planar).}
	\label{fig:world_map_bw}
\end{figure*}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=0.48\textwidth]{fig_regression_lambda_phi_linear.png}
	\caption{Plot of $\lambda$ vs $\phi$ by network type with regression lines.}
	\label{fig:regression_lambda_phi}
\end{figure}

@@

\begin{table}[htbp]
	\centering
	\caption{Summary statistics of planarity indicators across 100 square-mile samples of Oakland, California's drivable network.}
	\label{tab:samples_city}
	\input{table_samples_city.tex}
\end{table}

@@

\bibliographystyle{SageH}
\bibliography{references.bib}
